### 2023-01-15 tensor_clustering/ieee_revision/response_s2.tex

%     That's why we can not ``\emph{directly} obtain" the dTBM impossibility from TBM impossibility, as previous Remark 1 said. But we can ``\emph{easily}" obtain dTBM result by using the proof of TBM impossibility.

%     Note that there exists a set of parameters $(z^*, \mtheta^*, \tS^*)$ with $\mtheta^* = \mathbf{1}$ such that $(z^*, \mtheta^*, \tS^*) \in \tP_{\rm dTBM}(\gamma) \cap \tP_{\rm TBM}(\gamma)$. In the proof of TBM impossibility in \cite{han2020exact}, we eliminate the supreme by considering the special case with $(z^*, \mtheta^*, \tS^*)$ 
%     \begin{equation}
%         \inf_{\hat z: (\hat z, \hat \mtheta, \hat \tS) \in \tP_{\rm TBM}}  \sup_{(z, \mtheta, \tS) \in \tP_{\rm TBM}(\gamma)} p\ell(\hat z, z) \geq \inf_{\hat z: (\hat z, \hat \mtheta, \hat \tS) \in \tP_{\rm TBM}}    p\ell(\hat z, z^*)  > 1.
%     \end{equation}
%     Then, in dTBM, we also can eliminate the supreme by considering the same special case with $(z^*, \mtheta^*, \tS^*)$ 
%     \begin{equation}
%         \inf_{\hat z: (\hat z, \hat \mtheta, \hat \tS) \in \tP_{\rm dTBM}}  \sup_{(z, \mtheta, \tS) \in \tP_{\rm dTBM}(\gamma)} p\ell(\hat z, z) \geq \inf_{\hat z: (\hat z, \hat \mtheta, \hat \tS) \in \tP_{\rm dTBM}}    p\ell(\hat z, z^*)
%     \end{equation}
%     Notice that the infimum are taken under different regimes. We only need to show that 
%     \begin{equation}\label{eq:inf}
%         \inf_{\hat z: (\hat z, \hat \mtheta, \hat \tS) \in \tP_{\rm dTBM}}    p\ell(\hat z, z^*) = \inf_{\hat z: (\hat z, \hat \mtheta, \hat \tS) \in \tP_{\rm TBM}} p\ell(\hat z, z^*). 
%     \end{equation}
%     The equation~\eqref{eq:inf} is true. Because under $(z^*, \mtheta^*, \tS^*)$ with $\mtheta^* = \mathbf{1}$, it is equivalent to consider the UMP of the vector hypothesis test problem
%     \begin{equation}
%         H_0: \my = \mx_1 + \me \quad vs \quad H_1: \my = \mx_2 + \me,
%     \end{equation}
%     where $\mx_a$ are known centroids and $\me$ consists of i.i.d.\ $N(0,\sigma^2)$. By Neyman-Pearson Lemma, the UMP is the non-degree least square estimator $\hat z_{\rm UMP} = \argmin_{a \in \{1,2\}} \onormSize{}{\my - \mx_a}^2_F$, which is independent with the estimation $\hat \mtheta$. Then, we finish the proof
%     \begin{equation}
%         \inf_{\hat z: (\hat z, \hat \mtheta, \tS) \in \tP_{\rm dTBM}}    p\ell(\hat z, z^*) = p\ell(\hat z_{\rm UMP}, z^*) = \inf_{\hat z: (\hat z, \hat \mtheta, \tS) \in \tP_{\rm TBM}} p\ell(\hat z, z^*)  > 1
%     \end{equation}

%  \textbf{Claim:} The minimax errors over $\hat z$ and over $(\hat z, \hat \mtheta)$ are the same in our case; i.e.,
%     \begin{equation}
%         \inf_{\hat z: (\hat z, \hat \mtheta, \hat \tS) \in \tP_{\rm dTBM}} \sup_{(z^*, \mtheta^*, \tS^*) \in \tP_{\rm dTBM}(\gamma)} \ell(\hat z, z^*) =  \inf_{(\hat z, \hat \mtheta): (\hat z, \hat \mtheta, \hat \tS) \in \tP_{\rm dTBM}} \sup_{(z^*, \mtheta^*, \tS^*) \in \tP_{\rm dTBM}(\gamma)} \ell(\hat z, z^*).
%     \end{equation}

%     \textbf{Proof:} Note that the parts after the infimum are the same. Let $f(\hat z) = \sup_{(z^*, \mtheta^*, \tS^*) \in \tP_{\rm dTBM}(\gamma)} \ell(\hat z, z^*)$. Also note that for some parameters $x,y$, function $f$, and area $\mathbb{A}$ we use the notation
%     \begin{equation}
%         \{ x: f(x,y) \in \mathbb{A}\} \coloneqq \{ x: \text{there exists a } y \text{ such that } f(x,y) \in \mathbb{A}\} = \{x: \exists y \text{ s.t.} f(x,y) \in \mathbb{A} \}.
%     \end{equation}
%     It is equivalent to consider
%     \begin{equation}
%         \inf_{\hat z: \exists (\hat \mtheta, \hat \tS) \text{ s.t.} (\hat z, \hat \mtheta, \hat \tS) \in \tP_{\rm dTBM}}  f(\hat z) \quad \text{and} \quad \inf_{(\hat z, \hat \mtheta): \exists \hat \tS \text{ s.t.}  (\hat z, \hat \mtheta, \hat \tS) \in \tP_{\rm dTBM}} f(\hat z).
%     \end{equation}
%     Then, we have
%     \begin{align}
%          \inf_{(\hat z, \hat \mtheta): \exists \hat \tS \text{ s.t.}  (\hat z, \hat \mtheta, \hat \tS) \in \tP_{\rm dTBM}} f(\hat z) &=  \inf_{\hat z': \exists (\hat \mtheta, \hat \tS) \text{ s.t.} (\hat z', \hat \mtheta, \hat \tS) \in \tP_{\rm dTBM}}  \inf_{  \hat \mtheta': \exists \hat \tS \text{ s.t.} (\hat z', \hat \mtheta', \hat \tS) \in  \tP_{\rm dTBM} } f(\hat z')  \\
%          & =  \inf_{\hat z': \exists (\hat \mtheta, \hat \tS) \text{ s.t.} (\hat z', \hat \mtheta, \hat \tS) \in \tP_{\rm dTBM}} f(\hat z'),
%     \end{align}
%     where the last equation follows from the fact that $f(\hat z)$ is independent with $\hat \mtheta$. Therefore, we have proven the claim.

% \textbf{Claim:} Let $(z^*, \mtheta^*, \tS^*)$ denote the true parameters in Eqn (31). The hypothesis test corresponds to Eqn (32) should be 
%     \begin{equation}
%         H_0: \my = \theta^* \mx_1^* + \me, \quad vs \quad H_1: \my = \theta^* \mx_2^* + \me,
%     \end{equation}
%     where $\mx_a^* = [\Mat_1(\tS^* \times_2 \mM_2^* \times_2 \cdots \times_K \mM_k^*)]_{a:}$.

%     \textbf{Proof:} In all impossibility proofs (Eqn(32) in our proof, \cite{han2020exact}, and \cite{gao2018community}), we want to lower bound the following probability
%     \begin{equation}\label{eq:hypo}
%         \inf_{\hat z \in \tP} \{ \bbP(\hat z = 1| z^* = 2) + \bbP(\hat z = 2|z^* = 1) \},
%     \end{equation}
%     where the $\tP$ is the estimation space of $\hat z$ and $z^*$ is the true assignment. In our dTBM, we have $\tP = \{\hat z: (\hat z, \hat \mtheta, \hat \tS) \in \tP_{\rm dTBM}\}$, and the $\bbP(\cdot | z^*)$ should refer to the distribution of observation $\my$ with true parameter $z^*, \mtheta^*, \tS^*$, denoted as $\bbP(\cdot | z^*, \mtheta^*, \tS^*)$. Then, the hypothesis test corresponds to the probability~\eqref{eq:hypo} is 
%     \begin{equation}
%         H_0: \my = \theta^* \mx^*_1 + \me \quad vs \quad H_1: \my = \theta^* \mx_2^* + \me.
%     \end{equation}
%     The hypothesis test should not be affected by the estimation procedure of $\hat z$.

%     If we write the hypothesis test with unknown $\theta$
%     \begin{equation}
%         H_0: \my = \theta \mx^*_1 + \me \quad vs \quad H_1: \my = \theta \mx_2^* + \me,
%     \end{equation}
%     then we do not have a valid null/alternative distribution. In addition, from the estimation perspective, parameter $\mx_a$ is also unknown in dTBM problem.

%     \textbf{Claim:} Both \cite{han2020exact} and \cite{gao2018community} proves minimax bound
%     \begin{equation}\label{eq:minimax}
%         \inf_{\hat z} \sup_{(z, \tS, \mtheta) \in \tP(\gamma)} \bbE[p \ell(\hat z, z)] \geq 1,
%     \end{equation}
%     rather than the minimin bound
%     \begin{equation}\label{eq:minimin}
%          \inf_{\tS \in \tP(\gamma)} \inf_{\hat z} \sup_{(z, \mtheta)} \bbE[p \ell(\hat z, z)] \geq 1.
%     \end{equation}

%     \textbf{Proof:}

%     - For TBM \cite{han2020exact}, the parameter space is defined as 
%     \begin{equation}\label{eq:space}
%         \tP_{\rm TBM}(\gamma) = \tP_{\rm TBM} \cap \{\Delta_{\rm Euc}^2 \gtrsim p^{\gamma}\}.
%     \end{equation}
%     To prove the minimax rate~\eqref{eq:minimax}, we consider the boundary case $\tS^*$ such that $\Delta_{\rm Euc}^2(\tS^*) = p^{\gamma}$.

%     For minimin bound~\eqref{eq:minimin}, with any $\gamma$, we can always have 
%     \begin{equation}
%          \inf_{\tS \in \tP_{\rm TBM}(\gamma)} \inf_{\hat z} \sup_{z} \bbE[p \ell(\hat z, z)] \leq \inf_{\hat z} \sup_{z^*} \bbE[p \ell(\hat z, z^*)] \leq 0,
%     \end{equation}
%     where the inequality holds with true parameter $(z^*, \tS^*)$ which lies in the strong signal regime to exact recovery.

%   - For DCBM \cite{gao2018community}, we have parameter space 
%   \begin{equation}\label{eq:space_dcbm}
%       \tP_{\rm DCBM}(\gamma) = \tP_{\rm DCBM} \cap \{ \min_u B_{uu} - \max_{u \neq v} B_{uv} \geq p-q = \gamma \},
%   \end{equation}
%   where $\min_u B_{uu} - \max_{u \neq v} B_{uv}$ denotes the minimal difference between the diagonal and off-diagonal elements in the mean matrix, and $p-q$ can be considered as the SNR in this case.

%   To prove the minimax rate~\eqref{eq:minimax}, \cite{gao2018community} considers the boundary case where $\min_u B^*_{uu} - \max_{u \neq v} B^*_{uv} = p^* - q^*$.

%   For minimin bound~\eqref{eq:minimin}, with any $\gamma \in [0,1]$, ww can always have 
%   \begin{equation}
%       \inf_{B \in \tP_{\rm DCBM}(\gamma)} \inf_{\hat z} \sup_{z, \mtheta} \bbE[p \ell(\hat z, z)]  \leq \inf_{\hat z} \sup_{z^*, \mtheta^*} \bbE[p \ell(\hat z, z^*)] \leq 0,
%   \end{equation}
%   where the inequality holds with true parameters $B^*$ such that $p^* - q^*$ lies in the strong signal regime.

%   \textit{Therefore, the minimin bound~\eqref{eq:minimin} is trivial or meaningless under the TBM or DCBM case with parameter spaces~\eqref{eq:space} or \eqref{eq:space_dcbm}.}

%   - In our case, we have parameter space 
%   \begin{equation}
%       \tP_{\rm dTBM}(\gamma) = \tP_{\rm dTBM} \cap \{ \Delta_{\rm ang }^2 = p^{\gamma}\},
%   \end{equation}
%   For the minimax rate~\eqref{eq:minimax}, we consider the boundary case $(z^*, S^*, \mtheta^*) \in \tP_{\rm dTBM}(\gamma) \cap \tP_{\rm TBM}(\gamma)$.

%   However, the minimin rate~\eqref{eq:minimin} is not trivial for dTBM since $\tP_{\rm dTBM}(\gamma)$ does not include the $\tS^*$ that leads to arbitrarily large signal. If we revise the space as $ \tP_{\rm dTBM}'(\gamma) = \tP_{\rm dTBM} \cap \{ \Delta_{\rm ang }^2 \geq p^{\gamma}\}$, then the minimin rate is trivial as TBM and DCBM. This definition revision from $\tP_{\rm dTBM}$ to $\tP'_{\rm dTBM}$ won't affect results in old submissions but lead to an easier defense against the minimin rate comment.

%   \newpage

%   \textbf{Minimax vs Minimin rate.} The reviewer mention the minimax and minimin rate under the dTBM:
%   \begin{align}
%       {\rm Minimax:} \quad  \inf_{\hat z} \sup_{(z, \theta, S) \in \tP(\gamma)} \bbE[p l(\hat z,  z)] \geq 1\quad \quad 
%       {\rm Minimin:} \quad \inf_{S \in P(\gamma)} \inf_{\hat z} \sup_{(z, \theta) \in \tP(\gamma)} \bbE[p l(\hat z,  z)]\geq 1.
%   \end{align}
%   To analyze the minimax and minimin rate rigorously, we firstly recall and define several spaces for the estimator and true parameters.
%   \begin{enumerate}[wide]
%       \item $\tP_{\rm dTBM}, \tP_{\rm TBM}, \tP_{\rm DCBM}$: general parameter spaces for our dTBM, TBM \cite{han2020exact}, and matrix DCBM \cite{gao2018community};
%       \item $\tP_{\rm dTBM} (\gamma) = \tP_{\rm dTBM} \cap \{ \Delta_{\rm ang}^2 = p^{\gamma} \}$: dTBM parameter space with angle gap equal to $p^{\gamma}$;
%       \item $\tP_{\rm TBM} (\gamma) = \tP_{\rm TBM} \cap \{ \Delta_{\rm Euc}^2 = p^{\gamma} \}$: TBM parameter space with Euclidean gap equal to $p^{\gamma}$;
%       \item $\tP_{\rm DCBM} (\gamma) = \tP_{\rm TBM} \cap \{ \min_u B_{uu} - \max_{u \neq v} B_{uv} = \gamma \}$: DCBM parameter space with diagonal-offdiagonal gap equal to $\gamma$;
%       \item $\tP'_{\rm dTBM}(\gamma) = \tP_{\rm dTBM} \cap \{ \Delta_{\rm ang}^2 \geq  p^{\gamma} \}$:  dTBM parameter space with angle gap equal or \textbf{larger} than $p^{\gamma}$; similar for $\tP'_{\rm TBM}(\gamma)$ and $\tP'_{\rm DCBM}(\gamma)$;
%       \item $\tP_{z} = \{ z: c_1 p/r |z^{-1}(a)| \leq c_2 p/r \}$: space for all possible assignment satisfying the group size balance assumption; we omit the subscript $k$ for simplicity; $\tP_z$ should be the estimation space for $\hat z$ in dTBM, TBM, and DCBM, because all three models share the same balance constraint on $z$. 
%       \item $\tP_{\mtheta, {\rm dTBM}} = \{ \mtheta: \text{there exists } (z, \tS) \text{ such that } (z, \mtheta, \tS) \in \tP_{\rm dTBM}\}$: the space for all $\mtheta$ satisfying the dTBM requirement; similar to replace the subscript by $\tS$ or $(z,\mtheta)$ and similar to define $\tP_{\mtheta, {\rm dTBM}}(\gamma)$ and with other models.
%     \end{enumerate}
%   Equipped with these spaces, we re-state the minimax and minimin rates rigorously:
%   \begin{align}
%       {\rm Minimax:}& \quad  \inf_{\hat z \in \tP_z} \sup_{(z, \mtheta, \tS) \in \tP_{\rm dTBM}(\gamma)} \bbE[p \ell(\hat z,  z)] \geq 1 \label{eq:minimax} \\ 
%       {\rm Minimin:}& \quad \inf_{\tS \in \tP_{\tS, {\rm dTBM}}(\gamma)} \inf_{\hat z \in \tP_z} \sup_{(z, \mtheta) \in \tP_{(z,\mtheta), \rm dTBM}(\gamma)} \bbE[p \ell(\hat z,  z)]\geq 1. \label{eq:minimin}
%   \end{align}
%   Moreover, the space $\tP(\gamma)$ under the supreme can be replaced by the space $\tP'(\gamma)$, and these rates also holds for TBM and DCBM.

%   The comparison between minimax and minimin rates depends on spaces related to the signal; the minimax rates are invariant to the choice of $\tP(\gamma)$ and $\tP'(\gamma)$ while the minimin results are quite different with different spaces. The minimax rates under all models have been studied, so we focus on the minimin results here.

%   \begin{itemize}
%   \item \textbf{Choose $\tP'(\gamma).$} In \cite{han2020exact} and \cite{gao2018community}, we are actually using $\tP'(\gamma)$ rather than $\tP(\gamma)$. The minimin lower bound becomes meaningless under this case for all dTBM, TBM, and DCBM. We take TBM for detailed illustration.

%   \textbf{Claim:} For any $\gamma \leq 0$, 
%   \begin{equation}
%       \inf_{\tS \in \tP'_{\tS, {\rm TBM}}(\gamma)} \inf_{\hat z \in \tP_z} \sup_{z \in \tP'_{z, \rm TBM}(\gamma)} \bbE[p \ell(\hat z,  z)] = 0.
%   \end{equation}

%   The intuition is that we need to consider all $\tS^*$ with large signal in $\tP'(\gamma)$ due to the first infimum.

### 2023-01-15 tensor_clustering/ieee_revision/response_s2.tex

%   \textbf{Proof:} For any $\gamma \leq 0$, we always have $\tS^* \in \tP'_{\tS, {\rm TBM}}(\gamma)$ such that $\Delta_{\rm Euc}^2 (\tS^*) = c$ for some positive constant $c$. Then, we have 
%   \begin{align}
%       \inf_{\tS \in \tP'_{\tS, {\rm TBM}}(\gamma)} \inf_{\hat z \in \tP_z} \sup_{z \in \tP'_{z, \rm TBM}(\gamma)} \bbE[p \ell(\hat z,  z)] & \leq  \inf_{\hat z \in \tP_z} \sup_{z \in \tP'_{z, \rm TBM}(\gamma)} \bbE[p \ell(\hat z, z)| \Delta_{\rm Euc}^2(\tS^*) = c ]  \\
%       & \leq \sup_{z^* \in \tP'_{z, \rm TBM}(\gamma)} \bbE[p \ell(\hat z_{\rm alg}, z^*)| \Delta_{\rm Euc}^2(\tS^*) = c ]\\
%       & \leq 0,
%   \end{align}
%   where $\hat z_{\rm alg}$ refers to the algorithm output in \cite{han2020exact}, and the last inequality holds since the algorithm guarantee Theorem 3 or 4 hold with arbitrary $z^* \in \tP_z$ and $\tP'_{z, \rm TBM}(\gamma) = \tP_z$.

%       \item \textbf{Choose $\tP(\gamma).$} Our dTBM shows different conclusion with TBM and DCBM in this case.

%     %   \textbf{Claim:} For TBM and DCBM, the minimax is equal to the minimin rate; i.e., for example, 
%     %   \begin{equation}
%     %       \inf_{\hat z \in \tP_z} \sup_{(z, \tS) \in \tP_{z, \rm TBM}(\gamma)} \bbE[p \ell(\hat z,  z)]  =  \inf_{\tS \in \tP_{\tS, {\rm TBM}}(\gamma)} \inf_{\hat z \in \tP_z} \sup_{z \in \tP_{z, \rm TBM}(\gamma)} \bbE[p \ell(\hat z,  z)]. 
%     %   \end{equation}

%     %   \textbf{Proof:}

%   \end{itemize}

%   \textbf{Minimax rate of dTBM.} We consider the equivalent statement of the minimin/minimax rate under dTBM. We omit the subscript dTBM in $\tP$ here.

%   \begin{align}
%       \inf_{\tS \in \tP_{\tS}(\gamma)} \inf_{\hat z \in \tP_z} \sup_{(z, \mtheta) \in \tP_{z, \mtheta}(\gamma)} \bbE[p \ell(\hat z, z)] \geq 1  \Leftrightarrow  \text{for all } \tS^* \text{ s.t. } \Delta_{\rm ang}(\tS^*)^2 = p^{\gamma}, \inf_{\hat z \in \tP_z} \sup_{(z, \mtheta) \in \tP_{z, \mtheta}(\gamma)} \bbE[p \ell(\hat z, z)| \tS^*] \geq 1,
%   \end{align}
%   and similarly, 
%     \begin{align}
%       \inf_{(\mtheta, \tS) \in \tP_{\mtheta, \tS}(\gamma)} \inf_{\hat z \in \tP_z} \sup_{z \in \tP_{z}(\gamma)} \bbE[p \ell(\hat z, z)] \geq 1  \Leftrightarrow  \text{for all } (\mtheta^*, \tS^*) \in \tP_{\mtheta, \tS}(\gamma), \inf_{\hat z \in \tP_z} \sup_{z \in \tP_{z}(\gamma)} \bbE[p \ell(\hat z, z)| \mtheta^*, \tS^*] \geq 1.
%   \end{align}

%   The key step to prove the minimin or minimax rate is to lower bound error with given true parameters $(z^*, \mtheta^*, \tS^*)$ 
%   \begin{equation}
%       \inf_{\hat z \in \tP_z} \bbE[p \ell(\hat z, z)| z^*, \mtheta^*, \tS^*] \gtrsim \frac{1}{|T^c|} \sum_{i \in T^c}\inf_{\hat z \in \tP_Z} \bbP(\hat z(i) = 1| z^*(i) = 2, \mtheta^*, \tS^*) +  \bbP(\hat z(i) = 2| z^*(i) = 1, \mtheta^*, \tS^*),
%   \end{equation}
%   where $T^c$ is a set defined in \cite{han2020exact} and $|T^c| \asymp c_2$ for some constant $c_2$.

%   For any $i \in T^c$, the probability on the right hand side corresponding to the hypothesis test
%   \begin{equation}
%       H_0: \my = \mtheta^*(i) \mx^*_1 + \me, \quad \leftrightarrow \quad H_1: \my = \mtheta^*(i) \mx^*_2 + \me,
%   \end{equation}
%   and the best estimator is $\hat z_{LS}(i) = \argmin_{a = 1,2} \onormSize{}{\my - \mtheta^*(i) \mx^*_a} _F^2$ by Neyman-Pearson Lemma, where $\mx^*_a = \mat_1(\tS^* \times_2 \mTheta^* \mM^* \times \cdots \times_K \mTheta^* \mM^*)_{a:}$.

%   By the calculation in equation (102) in \cite{han2020exact}, we have 
%   \begin{equation}
%       \bbP(\hat z(i) = 1| z^*(i) = 2, \mtheta^*, \tS^*) +  \bbP(\hat z(i) = 2| z^*(i) = 1, \mtheta^*, \tS^*) \geq 2 \bbP \of{ N(0,1) \geq \frac{\onormSize{}{\mtheta^*(i) \mx^*_1 - \mtheta^*(i) \mx^*_2}_F}{\sigma}}.
%   \end{equation}
%   Due to the summation over $T^c$ and the number $(1,2)$ can be replace by any $(a,b), a \neq b$, we define $f(z, \mtheta, \tS) = \min_{i \in T^c, a \neq b}\onormSize{}{\mtheta(i) \mx_a - \mtheta(i) \mx_b}_F$. Then, we can lower bounded the rate $\inf_{\hat z \in \tP_z} \bbE[p \ell(\hat z, z)| z^*, \mtheta^*, \tS^*]$ by a constant when $f(z^*, \mtheta^*, \tS^*) \lesssim \sigma$. Hence, we re-state the minimax rates with $f.$

%   \begin{align}
%       &(1) \inf_{\hat \in \tP_z} \sup_{(z, \mtheta, \tS) \in \tP(\gamma)} \bbE[p \ell(\hat z, z)| \mtheta^*, \tS^*] \geq 1  \Leftrightarrow  \text{there exists a }(z^*, \mtheta^*, \tS^*)  \in \tP(\gamma) \text{ s.t. } f(z^*, \mtheta^*, \tS^*) \lesssim \sigma \\
%         &(2) \inf_{\tS \in \tP_{\tS}(\gamma)} \inf_{\hat z \in \tP_z} \sup_{(z, \mtheta) \in \tP_{z, \mtheta}(\gamma)} \bbE[p \ell(\hat z, z)| \mtheta^*, \tS^*] \geq 1   \\
%         & \quad \quad \Leftrightarrow  \text{for all } \tS^* \in \tP_{\tS}(\gamma), \text{ there exists a }(z^*, \mtheta^*)  \in \tP_{z, \mtheta}(\gamma) \text{ s.t. } f(z^*, \mtheta^*, \tS^*) \lesssim \sigma \\
%         &(3) \inf_{(\mtheta, \tS) \in \tP_{\mtheta, \tS}(\gamma)} \inf_{\hat z \in \tP_z} \sup_{z \in \tP_{z}(\gamma)}  \bbE[p \ell(\hat z, z)| \mtheta^*, \tS^*] \geq 1   \\
%         & \quad \quad \Leftrightarrow  \text{for all } (\mtheta^*, \tS^*) \in \tP_{\mtheta, \tS} (\gamma), \text{ there exists a }z^*  \in \tP_{z}(\gamma) \text{ s.t. } f(z^*, \mtheta^*, \tS^*) \lesssim \sigma.
%   \end{align}

%   (1) is easy to prove under both TBM and dTBM, since we only need to design a specific $(z^*, \mtheta^*, \tS^*)$ such that $   f(z^*, \mtheta^*, \tS^*) \leq \sigma$.

%   (2) is easy in TBM because $f(z, \mtheta, \tS) = \min \onormSize{}{\mx_a - \mx_b}_F \leq p^{(K-1)/2} \Delta_{Euc}$, and thus $f(z, \mtheta, \tS) \lesssim \sigma $ for any $\tS$ such that $\Delta_{Euc}^2(\tS) \leq p^{-(K-1)} \sigma^2$.

%   For (2) under dTBM, we consider the upper bound
%   \begin{align}
%       f(z^*, \mtheta^*, \tS^*) & = \min_{i \in T^c} \mtheta^*(i) \min_{a \neq b }\onormSize{}{\mx_a^* - \mx_b^*}_F \\
%       & \leq  \min_{i \in T^c} \mtheta^*(i) \min_{a \neq b } \onormSize{}{\mS^*_{a:} - \mS^*_{b:}}_F \lambda_{\max}^{K-1}(\mTheta^* \mM^*)   \\
%       & \leq \min_{i \in T^c} \mtheta^*(i) \min_{a \neq b } \onormSize{}{\mS^*_{a:} - \mS^*_{b:}}_F (\sqrt{\max_a \onormSize{}{\mtheta_{z^{-1}(a)}^* }^2})^{(K-1)}
%   \end{align}
%   where the last inequality follows from Lemma 6.

%   \newpage

%   \section{New minimax results}

%   Let $\tP_{\tS} \coloneqq \{ \tS: c_3\leq \onormSize{}{\text{Mat}(\tS)_{a:}}\leq c_4, a\in[r]\}$ denote space for core tensor $\tS$ under dTBM;  let $\tP_{z} \coloneqq \{ z: {c_1p\over r}\leq |z^{-1}(a)|\leq {c_2 p\over r}, a \in [r]\}$ denote the space for assignment $z$ under dTBM; let $\tP_{z ,\mtheta} \coloneqq \{ \mtheta\in\mathbb{R}^p_{+},\ 
% {c_1p\over r}\leq |z^{-1}(a)|\leq {c_2 p\over r}, \onorm{\mtheta_{z^{-1}(a)}}_1=|z^{-1}(a)|, a \in [r] \}$ denote the space for $(z, \mtheta)$ under dTBM,  where $c_1, c_2, c_3, c_4$ are constants in $\tP$.

%   \begin{lem}[Trivial statistical impossibility]\label{lem:trivial}  Consider general Gaussian dTBMs with parameter space $\tP(\gamma)$ with $K\geq 1$. Assume $ r =  o(p^{1/3})$. For any true core tensors $\tS^* \in \tP_{\tS} $ such that $\Delta_{\min}^2 (\tS^*)\leq 2$ (or equivalently $\gamma = 0$), no estimator $\hat z_{\text{stat}}$ achieves exact recovery in expectation under the worst case; i.e.,
%   \begin{equation}\label{eq:minminmax}
%   \liminf_{p \rightarrow \infty}\inf_{\tS^* \in  \tP_{\tS} \cap \{\Delta_{\min}^2(\tS^*) \leq 2\}}  \inf_{\hat z_{\text{stat}} \in \tP_z}\sup_{ (z^*, \mtheta^*) \in \tP_{z, \mtheta}} \bbE \left[ p\ell(\hat z_{\text{stat}}, z) \right]\geq 1.
% \end{equation}
%   \end{lem}

%   \begin{rmk}The Lemma~\ref{lem:trivial} indicates that for any possible $\tS^*$ with   $\Delta_{\min}^2 (\tS^*)\leq 2$ there exist parameters $(z^*, \mtheta^*)$ such that no estimator is able to exactly recover the assignment under the dTBM with true parameter $(z^*, \tS^*,\mtheta^*)$. Note that $\onormSize{}{\mv_1^s - \mv_2^s}^2_F \leq 2$ for arbitrary vectors $\mv_1, \mv_2$. Then, the regime $ \tP_{\tS} \cap \{\Delta_{\min}^2 (\tS^*)\leq 2\} = \tP_{\tS}$ includes all possible core tensor $\tS^*$ under dTBM. Hence, we say this minimax lower bound~\eqref{eq:minminmax} is trivial.
%   \end{rmk}

%   \begin{cor}[Statistical impossibility]\label{cor:impossible} Consider general Gaussian dTBMs with parameter space $\tP(\gamma)$ with $K\geq 1$.  Assume $ r < c p^{1/3}$ for some positive constant $c$. If the signal exponent satisfies $\gamma < -(K-1)$, then, for any true core tensor $\tS^* \in \tP_{\tS}$ such that $\Delta_{\min}^2 (\tS^*) = p^{\gamma}$, no estimator $\hat z_{\text{stat}}$ achieves exact recovery in expectation under the worst case; i.e.,
%   \begin{equation}
%   \inf_{\tS^* \in \tP_{\tS} \cap \{\Delta_{\min}^2(\tS^*) = p^{\gamma} \} }  \inf_{\hat z_{\text{stat}} \in \tP_z }\sup_{ (z^*, \mtheta^*) \in \tP_{z, \mtheta}} \bbE \left[ p\ell(\hat z_{\text{stat}}, z) \right]\geq 1.
% \end{equation}
%   \end{cor}

%   \begin{proof}[Proof of Corollary~\ref{cor:impossible}] Note that for any $\tS^*$
%   \begin{equation}
%       \{ (z, \mtheta): (z, \tS^*, \mtheta) \in \tP(\gamma) \} = \{ (z, \mtheta):  \mtheta\in\mathbb{R}^p_{+},\ 
% {c_1p\over r}\leq |z^{-1}(a)|\leq {c_2 p\over r}, \onorm{\mtheta_{z^{-1}(a)}}_1=|z^{-1}(a)|, a\in[r] \},
%   \end{equation}
%           which is independent with $\gamma$. Then, we have $\{ (z, \mtheta): (z, \tS^*, \mtheta) \in \tP(\gamma) \} = \{ (z, \mtheta): (z, \tS^*, \mtheta) \in \tP(0) \}$. 
%           Also note that $ \tP_{\tS} \cap \{\Delta_{\min}^2(\tS^*) = p^{\gamma} \} \subset  \tP_{\tS} \cap \{\Delta_{\min}^2(\tS^*) \leq 2\}$. Hence, we have 
%           \begin{align}
%                 & \inf_{\tS^* \in \tP_{\tS} \cap \{\Delta_{\min}^2(\tS^*) = p^{\gamma} \} }  \inf_{\hat z_{\text{stat}} \in \tP_z }\sup_{ (z^*, \mtheta^*): (z^*, \tS^*, \mtheta^*) \in \tP(\gamma)} \bbE \left[ p\ell(\hat z_{\text{stat}}, z) \right] \\
%                 & \quad \quad \geq \inf_{\tS^* \in \tP_{\tS} \cap \{\Delta_{\min}^2(\tS^*) \leq 2\}}  \inf_{\hat z_{\text{stat}} \in \tP_z}\sup_{ (z^*, \mtheta^*): (z^*, \tS^*, \mtheta^*) \in \tP(0)} \bbE \left[ p\ell(\hat z_{\text{stat}}, z) \right]\geq 1.
%           \end{align}
%   \end{proof}

%   \begin{proof}[Proof of Lemma~\ref{lem:trivial}] Consider the general asymetric dTBM~\eqref{eq:general_dtbm} in the special case that $p_k = p$ and $r_k = r$ for all $ k\in [K]$. For simplicity, we show the minimax rate for the estimation on the first mode $\hat z_1$; the proof for other modes are essentially the same.

%   To prove the minimax rate~\eqref{eq:minminmax}, it suffices to take an arbitrary $\tS^* \in  \tP_{\tS} \cap \{\Delta_{\min}^2(\tS^*) \leq 2\}$ and construct $(z^*, \mtheta^*)$ such that 
%   \begin{equation}
%       \inf_{\hat z_1 \in \tP_z} \bbE \left[ p\ell(\hat z_1, z_1^*) | z^*_k, \mtheta^*_k, \tS^*  \right]\geq 1.
%   \end{equation}

%   We consider the following construction:
%   \begin{enumerate}
%       \item[(i)] $\{z_k^*\}$ the same in \citet[Proof of Theorem 6]{han2020exact} with misclassification set $T^c_k \subset [p]$ and $|T^c_k| \asymp p/r$ for all $k \in [K]$.
%       \item [(ii)] $\{\mtheta_k^*\}$ such that $\mtheta_1^*(i) \leq \sigma r^{(K-1)/2} p^{-(K-1)/2}$ for all $i \in T_1^c$ and $\max_{k \in [K]/\{1\}, a \in [r]} \onormSize{}{\mtheta_{k, z^{*, -1}_k(a)}}^2_2 \asymp p/r$.
%   \end{enumerate}
%   % There exists a $(z^*, \mtheta^*) \in \tP_{z, \mtheta}$ satisfying the property (i) and (ii) when $r < p$; otherwise, when $r = p$, we must have $\mtheta^*(i) = 1$ due to the $\ell_1$ norm constraint and we can not satisfy the property (ii).

%   Then, following the proof of \cite{gao2018community}, we have 
%   \begin{equation}\label{eq:inf_lower}
%         \inf_{\hat z_1 \in \tP_z} \bbE \left[ \ell(\hat z_1, z_1^*) | z^*_k, \mtheta^*_k, \tS^*  \right] \geq \frac{1}{r^3 |T_1^c|} \sum_{i \in T_1^c} \inf_{\hat z_1 \in \tP_1} \{ \bbP[\hat z_1(i) = 1| z_1^*(i) = 2, \mtheta_k^*, \tS^*] +   \bbP[\hat z_1(i) = 2| z_1^*(i) = 1, \mtheta_k^*, \tS^*] \}. 
%   \end{equation}
